---
title: "How to provide input to the MAGNET website"
author: "Michiel van Dijk"
date: "`r Sys.Date()`"
output: pdf_document
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(readr)
library(knitr)
library(kableExtra)
```

# Introduction

In order to share information about the MAGNET model, related publications, projects and blogs, and team members, we created a new MAGNET website. The website is built using a combination of Hugo and RStudio. We have chosen for this approach over other options, such as Wordpress, because it is relatively simple to create an 'academic' website that has all the basic features to showcase our work, in particular:

- Overview of publications that can easily be updated
- Search function
- Tags
- Overview of team members
- Possibility to easily add equations

Furthermore, building and updating the website resembles working with MAGNET as it involves (basic) coding and versioning and therefore should fit very well with DNA of the MAGNET team. More specifically, to build the website, one needs to use Markdown language, which resembles LATEX (but much simpler), which is subsequently rendered into a html that produces the website. More information on the approach can be found here:

- [Demo of academic website](https://themes.gohugo.io/theme/academic/)
- [How to build an academic site with Hugo](https://wowchemy.com/)
- [How to build an Hugo website using the R Blogdown package](https://bookdown.org/yihui/blogdown/)
- [Example of personal website build using the proposed approach](https://www.michielvandijk.org/)
- [Draft MAGNET website](https://magnet-model.netlify.app/)


# Types of input requested from MAGNET team members

Four types of input are requested from the team members (click to go to the website):

- [Ongoing and past research projects](https://www.magnet-model.eu/research/)
- [Team member entry](https://www.magnet-model.eu/team/)
- [Publications](https://www.magnet-model.eu/publication/)
- [News](https://www.magnet-model.eu/post/)

In all four cases, information can very easily supplied by adding (mostly already existing) information to a very simple text template. More details on how to do this are presented below. The templates can be found on the MAGNET sharepoint in the templates folder: `MAGNET - Documents\6 - MAGNET website\templates`


## Ongoing and past research projects

The website shows summaries of ongoing and past research projects, which are meant to showcase our work. In most cases the content can be copied from project proposals, interim reports of deliverables (including journal articles). Preferably at least one key image is added that best describes the project. To add a new project, please provide/do the following:

- Create a new subfolder on the sharepoint: `MAGNET - Documents\6 - MAGNET website\_projects_to_be_added`. Please use a short name without capitals and instead of spaces use '_'.
- Fill out the project template file that can be found here: `MAGNET - Documents\6 - MAGNET website\templates\projects\index.md`and save it in the project folder you just created. Please do NOT change the name of the `index.md` file - it has to be named index.md. *.md files are text files that can edited with Notepad, Word or simular word processing software. The minimum content of the file is the title and an abstract but in case it is relevant also please provide the name of a team member to contact for more information and relevant publications - see example in the template file. 
- Provide one key picture that illustrate the project. Simply save it as `featured.png` (only *.png format is allowed) in the project folder. This picture will be (a) automatically added to the project 'card' in the Research window and (b) put on top of the project description.  
- Optionally, provide other pictures, which can be added to the project description. To do this save the relevant pictures in the project folder and add the code to load them. See the template for examples.
- Inform Michiel (michiel.vandijk@wur.nl) and/or Thijs (thijs.delange@wur.nl) you have want to add a new project.


## Publications

The website lists all MAGNET-related publications. To add a new publication, please provide/do the following:

- Add relevant information about the publication in the following file: `MAGNET - Documents\6 - MAGNET website\_publications_to_be_added\list_of_publications_to_be_added.docx`
- When possible __always__ add the DOI of the publication as this makes it possible to automatically retreive all relevant information from a global publications database. 
- Inform Michiel (michiel.vandijk@wur.nl) and/or Thijs (thijs.delange@wur.nl) you have want to add a new publication.


## News

The website shows brief information on MAGNET-related news, such as the launch of a new report that features MAGNET-based results, the acquisition of a new project and reference to MAGNET research in the media. To add a new news item, please provide/do the following:

- Create a new subfolder on the sharepoint: `MAGNET - Documents\6 - MAGNET website\_news_to_be_added`. Use the following structure for naming the folder; start with the date using this format: YYYY-MM-DD-short-description. Use '-' instead of spaces.
- Fill out the news template file that can be found here: `MAGNET - Documents\6 - MAGNET website\templates\news\index.en.md`and save it in the project folder you just created. Please do NOT change the name of the `index.en.md` file - it has to be named index.en.md. *.md files are text files that can edited with Notepad, Word or simular word processing software.  
- Provide one key picture that illustrate the project. Simply save it as `featured.png` (only *.png format is allowed) in the project folder. This picture will be (a) automatically added to the news 'card' in the Research window and (b) put on top of the news item.  
- Optionally, provide other pictures, which can be added to the project description. To do this save the relevant pictures in the project folder and add the code to load them. See the template for examples.
- Inform Michiel (michiel.vandijk@wur.nl) and/or Thijs (thijs.delange@wur.nl) you have want to add a new project.



## Team member entry

The website shows the picture and key information (e.g. name, position, key interests, bio, cv, links to research gate, WUR personal website etc.) of all MAGNET team members. To add a new team member or update your information, please provide/do the following:

Create a new subfolder on the sharepoint: `MAGNET - Documents\6 - MAGNET website\team` in case you are a new team member or navigate to the folder with your name if you want to update your personal information. 
- In case of new team members, fill out the team member template file that can be found here: `MAGNET - Documents\6 - MAGNET website\emplates\team_member\_index.md` and save it in the project folder you just created. Please do NOT change the name of the `_index.md` file - it has to be named _index.md. *.md files are text files that can edited with Notepad, Word or simular word processing software.  
- Provide one key picture that illustrate the project. Simply save it as `featured.png` (only *.png format is allowed) in the project folder. This picture will be (a) automatically added to the news 'card' in the Research window and (b) put on top of the news item.  
- Optionally, provide other pictures, which can be added to the project description. To do this save the relevant pictures in the project folder and add the code to load them. See the template for examples.
- Inform Michiel (michiel.vandijk@wur.nl) and/or Thijs (thijs.delange@wur.nl) you have want to add a new project.


- Add your details in the template found here and save it under your initials (without dots, etc) in this folder

To create a first version of the website, we need to following four files from each team member (also see table):

- *Personal information.* All personal information (except for the picture) is stored in _index.md. Please update the following items only: (1) title, (2) role, (3) interests, (4) education, (5) social (remove the entries that are not relevant for you, e.g. linkedin), (6) cv (use your name in filename), (7) biography (add your own). The files use Markdown which is a general markup language that can be used to layout text, add equations, etc For examples see [here](https://themes.gohugo.io//theme/academic/post/writing-technical-content/). For a cheatsheet with the main options see [here](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet).

- *Picture/avatar.* Save your picture as 'avatar.jpg'

- *CV.* Save your cv as '[your full name].pdf' (see note on which name to use below!).

- *Publications.* We want to create one file with all MAGNET related publications, which can be uploaded to the website. We already prepared a reference list, which can be found on the [website](https://magnet-model.netlify.app/publication/). Please send us any publications that are still missing. Reference software such as Mendeley, Endnote or Zotero can save a reference list in bibtex (.bib) format. In case you use this type of software please save the reference list as '[your full name].bib'. In case you are not using reference software, provide a Word file but, where possible, add the DOI of each publication.  

```{r echo = FALSE, message = FALSE, warning = FALSE}
website_files <- read_csv(here("team_input/_template/website_files.csv"))
kable(website_files, booktabs = TRUE, 
      linesep = "", 
      caption = "MAGNET website files needed for each team member") %>%
  kable_styling(latex_options =c("hold_position")) %>%
  column_spec(1:3.,width = c("4cm", "2.5cm", "8cm"))
  
```

Please store the requested file in the WEBSITE 2020 folder on the sharepoint. For the link click [here](https://sharepoint.wur.nl/sites/MAGNET/_layouts/15/start.aspx#/SitePages/Home.aspx?RootFolder=%2Fsites%2FMAGNET%2FShared%20Documents%2FWEBSITE%202020&FolderCTID=0x012000EA99BD9A9D6F634DA6A91C2575D3647C&View=%7B90D00A8E%2D9A44%2D4ABA%2DA606%2DF810D4BB1007%7D). We will use this location to collect all information for the website.  

To prepare your files, do the following:

- Create a new subfolder using your full name (lowercase) as folder name in the `team` subfolder. Note that the name of this folder will be used as user name to make automatic links with your name in the publications list. Similarly, your user name will also be used to identify your cv and other files that belong to your file. Hence, each time when you have to add your name (i.e. folder name, in the _index.md file, CV file name, bib file and possibly more locations) always write it in the same way and preferably use 'the version' that is most frequently used in your publications (e.g. full name without initials of middle name). In case this differs across publications, it is possible to edit the reference file in order to use one standardized version based on the user name. It is allowed to use spaces in user name (and file names) but use lowercase only.
- Copy the files from the `_template` folder to your own folder.
- Update the `_index.md` file and replace the `avatar.jpg`, `[your name].pdf` and `[your name].bib` files

Regularly (e.g. every six months) we will copy these files to right location in the website folder after which the website will be automatically updated. We can easily make additional updates so please inform us if you have made changes to your profile (or other parts of the website) and want these to be copied to the website. 


# Questions

Please do not hesitate to contact me if anything is unclear, you want to update the MAGNET website yourself using Hugo/RStudio or if you want to create your own personal website.

Michiel

michiel.vandijk@wur.nl
+31 70 3358 341




